
## Chapter 4 : Arithmetics

### 0.Contents

1. Using R as a calculator
2. Constructing and working with vectors
3. Vectorized calculations

### 1.Context

 - Statistical analysis involves a lot of calculations and that's what R does best
 - R goes far beyond employing the classic arithmetic operators/functions by applying vectorized operations to a vector w/o requiring loop over it



### 2.Numbers

#### 2.1 Basic Arithmetics



##### 2.1.1 Arithmetics operators

sum, rest, multiplication, division, power, mod, int div 


```{r echo=TRUE}



2+3 


8-2

3*2

10/5

2^3

7%%3

7%/%3


```


##### 2.1.2 Vectorizing

To see how this work lets considers an All-Star Basket Game Donation Event
Vectors represent number of baskets for the 5 games.
For each basket of Granny---> 120$
For each basket of Geraldine 145$

 
```{r echo=TRUE}
baskets.of.Granny <- c(12,4,4,6,9,3)
baskets.of.Geraldine <- c(5,3,2,2,12,9)
Granny.money <- baskets.of.Granny *120
Granny.money
Geraldine.money <- baskets.of.Geraldine * 145
Geraldine.money
total.money<-Granny.money + Geraldine.money

total.money



```



## 2.2 Math Functions



Some of the mathematical functions in R (There are thousands)

abs(x)
log(x, base=y)
exp(x)
sqrt(x)
factorial(x)
choose(x,y)

```{r echo=TRUE}
abs(-3)
log(9, base=3)
exp(1)
sqrt(8)
factorial(5)
choose(6,2) # 6!/((6-2)!2!)
```


### Log/Exp Functions

```{r echo=TRUE}


log(1:3) # vectorized
log(1:3,base=6) # vectorized
log10(500)
log2(1024)

x<-log(1:5) # vectorized
x
exp(x) # vectorized
```



