
## Chapter 4 : Arithmetics

### 0.Contents

1. Using R as a calculator
2. Constructing and working with vectors
3. Vectorized calculations

### 1.Context

 - Statistical analysis involves a lot of calculations and that's what R does best
 - R goes far beyond employing the classic arithmetic operators/functions by applying vectorized operations to a vector w/o requiring loop over it



### 2.Numbers

#### 2.1 Basic Arithmetics



##### 2.1.1 Arithmetics operators



```{r echo=TRUE}

2+3


8-2

3*2

10/5

2^3

7%%3

7%/%3


```


##### 2.1.2 Vectorizing

To see how this work lets considers an All-Star Basket Game Donation Event
Vectors represent number of baskets for the 5 games.
For each basket of Granny---> 120$
For each basket of Geraldine 145$

 
```{r echo=TRUE}
baskets.of.Granny <- c(12,4,4,6,9,3)
baskets.of.Geraldine <- c(5,3,2,2,12,9)
Granny.money <- baskets.of.Granny *120
Granny.money
Geraldine.money <- baskets.of.Geraldine * 145
Geraldine.money
total.money<-Granny.money + Geraldine.money

total.money



```



## Including Plots

You can also embed plots, for example:

